\Trill: Secure firewall-traversing networking

### 2012-12-14 6.858/paper/paper.tex
Client mumble

\subsection{Trill client library}

>>>>

\subsection{Trill client library}
The \Trill client library is fairly straightforward. Its job is simply to open a
UDP socket, perform a \verb`chownat`-like discovery protocol (which we call
``probing''), and then perform a DTLS handshake. The probing protocol is the
only non-obvious part of this. In particular, since TLS demands that one party
act as the server and the other as the client, the probing protocol must somehow
decide on a winner and a loser. Unfortunately, a result from the distributed
systems literature tells us that it is impossible for two parties to both agree
on even a single bit of information on a lossy out-of-order channel like UDP, so
the cause seems like a lost one. However, in practice, it is possible to use
DTLS's retry behavior, combined with non-colliding message types and
drop-on-error packet parsing semantics, to work around this. Both parties
generate random 64-bit numbers, and the client with the larger number is the
winner. If a client discovers it is the winner, it transitions to the ``server''
state, in which it attempts to read (and parse) DTLS handshake records, but
continues to send probes to its peer at regular intervals. If a client discovers
that it is the loser, and that its peer has acknowledged this fact (an extra bit
in the message), it transitions to ``client'' mode, in which it attempts a DTLS
handshake, discarding probe packets it receives. The asymmetry around the
acknowledge bit and the timeouts allow us to guarantee protocol progress in the
limiting case.

We wanted the \Trill client library to be as flexible as possible, and a large
portion of the implementation effort was spent making sure the library was
separated from both the particulars of the event loop implementation and the
choice of cryptographic library. Clients of \Trill must pass in a table of
function pointers which allow \Trill to be notified of various event loop
events, such as socket read/write availability and timers.  Secondly, the choice
of cryptographic library is controllable via a preprocessor flag, and \Trill
implementations can provide several of them in the hopes of greater
compatibility. Although we only provided implementations for Glib and GnuTLS
(the libraries that \verb`libpurple`, a popular instant messaging application
uses, which was the use case we originally envisioned for \Trill), a brief
perusal of the APIs for \verb`libev`, \verb`libevent`, OpenSSL, and NSS confirms
that the abstractions we expose in \Trill are sufficiently general to allow any
combination of event loop and TLS implementation to be used.
